---
title: "How to use package {xmlprocessor}"
author: "Benjamin Louis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(xmlprocessor)
```


# Fill a xml template

One of the main goal of package {xmlprocessor} is to facilitate the serial creatoin of xml file. From a xml template, you can use a dataframe to replace text and attribute values.

Starting with the creation and printing of a template :

```{r}
library(xml2)
template <- read_xml("<parent>
                        <child nom='child1'>
                          <grandchild>grandchild1</grandchild>
                          <grandchild>grandchild2</grandchild>
                        </child>
                        <child nom='child2'>
                          null
                        </child>
                      </parent>")
print(template)                   
```

The xml template contains 4 values that can be changed : grandchild1, grandchild2, child1 and child2. The first two are texts and the two latter are attributes values.

To fill the template with different values, you can build a dataframe where the columns names are the exact text to be replaced. For text values, this should be the whole text between xml element (<...>thistext</...>) and for attributes values, this should be the whole text between quotes.


```{r}
toreplace <- data.frame(child1 = c("Ben", "Thomas"), child2 = c("Sarah", "Marie"),
grandchild1 = c("Brad", "Angelica"), grandchild2 = c("Jude", "Lea"))
toreplace
```

You can then fill the template with information contained in `toreplace` to create a list with two xml documents with the structure as `template` but where grandchild1, grandchild2, child1 and child2 are replaced by the corresponding values in `toreplace`.

```{r}
# No export, no collapsing
newxml <- xml_fill_template(xmltemplate = template, with = toreplace)
print(newxml[[1]])
print(newxml[[2]])
```

It is also possible to collapse the filled xml documents ont a big one by specifying a root node name with the `collapse` argument. Note that if the given root node name is als the root node name of `template`, the latter must contain only one child (which can contains several children and so on).

```{r}
# Export and collapsing
newxml <- xml_fill_template(xmltemplate = template, with = toreplace, collapse = "grandparent")
print(newxml)
```

Eventually, you can export the xml document by specifying a path to a folder with the `export` argument and a name (or names) of the xml file(s) exported with the `name` argument.
